### 2021-08-25 plos_latex_template.tex
RJ: changes in accessibility rule

\section{Rule X: Make the conference accessible to all, from start to end}
\label{rule_accessibility}
Conferences are often inaccessible to people with hearing, visual, and other disabilities \cite{priceAccessImaginedConstruction2009}. %People may also find conferences inaccessible due to their caring responsibilities, dietary restrictions, religious practices, or LGBTQ+ status.
Inaccessible practices exclude people from conferences, while accessible practices are inclusive and can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general.

>>>>

\section{Rule X: Make the conference accessible to people with disabilities}
\label{rule_accessibility}

Conferences are among the least accessible spaces that people with disabilities may encounter \cite{priceAccessImaginedConstruction2009}.
%People may also find conferences inaccessible due to their caring responsibilities, dietary restrictions, religious practices, or LGBTQ+ status.
Ironically, accessibility practices are inclusive not only for people with disabilities but can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general.
